### 2018-01-25 ApproxComp/sec-beyond.tex

There exist no single techniques fit all for big data analytics, and  it is often necessary to combine different techniques to obtain satisfiable solutions. 
We have seen that data sampling and data compression techniques help to achieve a balance between efficiency and effectiveness. 
We next roughly introduce three other potential techniques used for big data analytics.

When there are data updates, query answers typically need to be re-computed to reflect the changes. Incremental computation is a technique that attempts to reduce computations by reusing previous computing efforts and only computing those answers that ``depend on'' the changed data.

 incremental algorithms have been developed for
various applications.  Thomas W. Reps has done pioneering work on the study of incremental computation, and he observed that
the complexity of incremental algorithms was more accurately characterized
in terms of the size of the area affected by the updates, rather than the size
of the entire input~\cite{Reps96}.

One may notice that incremental algorithms can be utilized to achieve query approximation.

Data partitioning, Data indexing and Distributed computing~\cite{MaLHLH16} can also be combined to design query approximation and data approximation approaches for big data analytics.

>>>>

  For big data analytics, there are no one-size-fits-all techniques.  it is often necessary to combine different techniques to obtain good solutions.
We have seen that data sampling helps to achieve a balance between efficiency and effectiveness for link prediction,
and other techniques, \eg incremental computation, data partitioning, data indexing and distributed computing~\cite{MaLHLH16} can
also be unitized to  design query and data approximation techniques for big data analytics. 
For instance, it is easy to see that incremental algorithms can be utilized to achieve query approximation.

### 2018-01-25 ApproxComp/sec-conclusion.tex

In this article we have introduced approximation computation techniques toward efficient and effective big data analytics.

First we see the importance of graph search by investigating the applications in industry, academia research developments, and the historical development of search.
And then, we have introduced and analyzed three types of graph search: cohesive subgraph,keyword search on graphs and graph
pattern matching. Finally, we have pointed out the problems and challenges graph search confronts and presented some useful techniques to deal with the problems.\par
\, As a a new paradigm for social computing, graph search has received extensive attentions. However, there are still a lot of questions to be solved in graph search, which is also a challenge for us.\par

>>>>

In this article we have systematiclly introduced approximation computation techniques toward efficient and effective big data analytics.
Furthermore, although approximate computation does not put
theoretical bounds with respect to optimal solutions, it does expect a balance between efficiency and accuracy. Indeed, (1) our query approximation techniques~\cite{tods-MaCFHW14,LinMZWH17,MaHWLH17} show that efficiency can be obtained efficiency with high accuracy in practice, and (2) our data approximation techniques for shortest paths and distances and link prediction~\cite{MaFLWCH16,DuanMAMH17} show that efficiency and accuracy can be obtained for certain data analytic tasks. That is, the design policy approximate computation of is not to sacrifice accuracy for efficiency, but to achieve both efficiency and effectiveness in practice.

### 2018-01-25 ApproxComp/sec-data.tex

We show experimentally that about $1/3$  nodes of social networks and road networks  are captured by by proxies, leaving $2/3$ in the reduced graphs.
Hence, we propose a light-weight data reduction technique for speeding-up (exact)  shortest path and distance queries on large weighted undirected graphs~\cite{MaFLWCH16}.

without losing any accuracy

@@

Link prediction methods are often applied to very large and sparse networks, which has a large {\em search space} $O(n^2)$, 
where $n$ is the number of nodes. Hence, the scalability is a big challenge. In fact, an often overlooked fact is that most {\em exiting link prediction algorithms evaluate the link propensities only over a subset of possibilities rather than all propensities over the entire network}, \eg \cite{zhu2016}.
In order to understand why this is the case, consider a large network with $10^8$ nodes. Its number of {\em possibilities} for links
is of the order of $10^{16}$. Therefore, a 3GHz processor would
require at least $35$ days just to allocate one {\em machine cycle} to
every pair of nodes. This implies that in order to determine the
top-ranked link predictions over the {\em entire network}, the
running time will be much much larger than $35$ days.

@@

\eat{%%%%%%%
\begin{table}
\caption{The $O(n^2)$ problem in link prediction: Time required to
allocate a {\em single machine cycle} to every node-pair possibility
in networks of varying sizes and processors of various speeds.}
\label{time}
\vspace{0ex}
\centering
\begin{tabular}{cccc}
\hline \hline Network Sizes & 1 GHz &  3 GHz & 10 GHz \\
\hline \hline $10^6$ nodes & 1000 sec. & 333 sec. & 100 sec.\\
\hline $10^7$ nodes & 27.8 hrs &  9.3 hrs &  2.78 hrs\\
\hline $10^8$ nodes & $>100$ days &  $>35$ days & $> 10$ days\\
\hline $10^9$ nodes & $>10000$ days & $>3500$ days & $> 1000$ days\\
\hline \hline
\end{tabular}
\vspace{-2ex}
\end{table}
}%%%%%%%%%%%

To this end, we explore an {\em ensemble approach} to
achieving the aforementioned goals.

We show how to make latent factor models
practical for link prediction by decomposing the search space into a
 set of smaller matrices. As a result, large parts of the $O(n^2)$
search space can be pruned without even having to evaluate the
relevant node pairs. An optimizing method is also provided for
speeding up the search process when a threshold is available.
This provides an efficient approach for the
top-$k$ problem in link prediction.

Furthermore, our problem
decomposition method is an ensemble approach enabled with three
structural bagging methods with performance guarantees, which has obvious {\em
effectiveness} advantages. By incorporating with the characteristics of  link prediction, the bagging methods maintain high prediction
accuracy while reducing the network size via graph sampling techniques.
Note that the same bias-variance
tradeoffs apply to the link-prediction problem, as they apply to the
standard classification problem. Therefore, the use of an ensemble
approach has obvious effectiveness advantages as well.

Using real-life datasets, we finally conduct an extensive experimental study, and show that our ensemble approach for link prediction is both effective and efficient.

>>>>

We show experimentally show that about $1/3$  nodes of real-life social networks and road networks  are captured by by proxies, leaving $2/3$ in the reduced graphs.
Hence, we propose a light-weight data reduction technique for speeding-up (exact)  shortest path and distance queries on large weighted undirected graphs~\cite{MaFLWCH16}.

@@

Link prediction methods are often applied to very large and sparse networks, which has a large {\em search space} $O(n^2)$, 
where $n$ is the number of nodes. Hence, the scalability is a big challenge. In fact, an often overlooked fact is that most {\em exiting link prediction algorithms evaluate the link propensities only over a subset of possibilities rather than all propensities over the entire network}.
In order to understand why this is the case, consider a large network with $10^8$ nodes. Its number of {\em possibilities} for links
is of the order of $10^{16}$. Therefore, a 3GHz processor would
require at least $35$ days just to allocate one {\em machine cycle} to
every pair of nodes. This implies that in order to determine the
top-ranked link predictions over the {\em entire network}, the
running time will be much much larger than $35$ days.

@@

Latent factor models have been shown to be wildly successful in the domain of
collaborative filtering, but not link prediction in spite of the obvious
similarity between link prediction and collaborative filtering and
the obvious effectiveness of latent factor models. One of the reasons why latent factor models are rarely used for
link prediction is due to their complexity. In
collaborative filtering applications, the item dimension is of the
order of a few hundred thousand, whereas even the smallest  real-world networks contain more than a million nodes.
Even worse, we also experientially find that the quality of link prediction for latent factor models decreases with the increase of data sparsity,
and networks typically become sparser when their sizes grow larger.

\eat{%%%%%%%

The factorization of a matrix of
size $O(n^2)$ is not only computationally expensive, but also
memory-intensive.  As will be seen later in this article, one advantage
of  latent-factor models is that they are able to  transform the
adjacency matrix to a multidimensional space which can be searched
efficiently {\em by pruning} large portions of the $O(n^2)$ search
space in order to recommend the top-$k$ possibilities.

\begin{table}
\caption{The $O(n^2)$ problem in link prediction: Time required to
allocate a {\em single machine cycle} to every node-pair possibility
in networks of varying sizes and processors of various speeds.}
\label{time}
\vspace{0ex}
\centering
\begin{tabular}{cccc}
\hline \hline Network Sizes & 1 GHz &  3 GHz & 10 GHz \\
\hline \hline $10^6$ nodes & 1000 sec. & 333 sec. & 100 sec.\\
\hline $10^7$ nodes & 27.8 hrs &  9.3 hrs &  2.78 hrs\\
\hline $10^8$ nodes & $>100$ days &  $>35$ days & $> 10$ days\\
\hline $10^9$ nodes & $>10000$ days & $>3500$ days & $> 1000$ days\\
\hline \hline
\end{tabular}
\vspace{-2ex}
\end{table}
}%%%%%%%%%%%

We explore an {\em ensemble approach} to make latent factor models
practical for link prediction by decomposing the search space into a
 set of smaller matrices with three structural bagging methods with performance guarantees, which has obvious {\em
effectiveness} advantages. In this way, latent factor models only need to deal with networks with small sizes (and denser), and retain
their effectiveness and efficiency.  By incorporating with the characteristics of  link prediction, the bagging methods maintain high prediction
accuracy while reducing the network size via graph sampling techniques. 
Further, the same bias-variance tradeoffs apply to the link-prediction problem, as the
standard classification problem. Therefore, the use of an ensemble
approach has obvious robustness advantages as well.

We experimentally show that our ensemble approach is over $50$ times faster and  over $20\%$ more accurate than {\sc bigclam} \cite{yang-wsdm2013} on using real-life social networks.

### 2018-01-25 ApproxComp/sec-query.tex

To lower the high complexity of subgraph isomorphism, substitutes for subgraph isomorphism~\cite{FanLMTWW10,FanLMTW11} that allow graph pattern matching to be conducted in cubic-time have been proposed by extending graph simulation~\cite{infsimu95}. However, they fall short of capturing the topology of data graphs, i.e., graphs may have a structure drastically different from pattern graphs they match, and the matches found are often too large to analyze.

>>>>

To lower the high complexity of subgraph isomorphism, substitutes for subgraph isomorphism \cite{FanLMTWW10,FanLMTW11}, that allow graph pattern matching to be conducted in cubic-time have been proposed by extending graph simulation~\cite{infsimu95}. However, they fall short of capturing the topology of data graphs, i.e., graphs may have a structure drastically different from pattern graphs they match, and the matches found are often too large to analyze.
